Graphical Tests for Power Comparison of Competing Designs

### 2012-03-28 comparison.tex
re-structuring, focus on first example
discussion of first experiment
small restructuring
re-working first paragraph - yep still! added more references.

\usepackage{natbib}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
\usepackage{amsmath}

%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Lendie Follett, Heike Hofmann, Mahbub Majumder, Dianne Cook}
\authorfooter{
%% insert punctuation at end of each item
\item
 Lendie Follett is a graduate student in Statistics at Iowa State University, E-mail: lfollett@iastate.edu.
\item
everybody else is at Iowa State University, too
}

@@

\input{experiment}

\section{Conclusion}

>>>>

\usepackage{natbib}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage[table]{xcolor}
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Lendie Follett, Heike Hofmann, Mahbubul Majumder, Dianne Cook}
\authorfooter{
%% insert punctuation at end of each item
\item
 Lendie Follett is an undergraduate student in Statistics at Iowa State University, E-mail: lfollett@iastate.edu.
\item
 Heike Hofmann is an associate professor in Statistics at Iowa State University, E-mail: hofmann@iastate.edu.
\item
 Mahbubul Majumder is a graduate student in Statistics at Iowa State University, E-mail: mahbub@iastate.edu.
\item
 Dianne Cook is a full professor in Statistics at Iowa State University, E-mail: dicook@iastate.edu.
}

@@

\input{setup}
\input{experiment}
\input{experiment-two}
\input{conclusions}

### 2012-03-28 intro.tex
re-working first paragraph - yep still! added more references.

% !TEX root = comparison.tex
%% \section{Introduction} %for journal use above \firstsection{..} instead
%We introduce and discuss a tool for comparing different charts that are renderings of the same data in order to evaluate them for efficiency.
So, you've just spent countless hours, burning the late night candle
wax, and discovered several astonishing features in the data. Your
exploratory graphics are quick to produce, interactive, flexible,
fabulous for discovery, but now you need to present the information to
your boss, the co-workers, a class of students, or get it published in
that top-rated journal. Those exploratory graphics are unlikely to
communicate the discovered information to your audience efficiently,
or elegantly.  To decide on the best way to present the specific
information there can be many types of plots to choose from. The
decision process is assisted by past experience, personal aesthetic
preferences, the characteristics of the audience, and a good working
knowledge of general perceptual strengths and weaknesses
\citep{cleveland:1984,heer:2010}. Perceptual studies are thinly spread
for data visualization, and have, and will probably, only cover very
broad perceptual principles. Faced with design decisions for a very
specific task requires a closer level of detail. Focus groups
\citep{Mazza07} can find small problems with designs and move us
closer to a final handful of possible designs, but they lack broad
audience validatity and objective evaluation.

>>>>

% !TEX root = comparison.tex
%% \section{Introduction} %for journal use above \firstsection{..} instead
%We introduce and discuss a tool for comparing different charts that are renderings of the same data in order to evaluate them for efficiency.
So, you've just spent countless hours, burning the late night candle
wax, and discovered several astonishing features in the data. Your
exploratory graphics are quick to produce, interactive, flexible,
fabulous for discovery, but now you need to present the information to
your boss, the co-workers, a class of students, or get it published in
that top-rated journal. Those exploratory graphics are unlikely to
communicate the discovered information to your audience efficiently,
or elegantly.  To decide on the best way to present the specific
information there can be many types of plots to choose from. The
decision process is assisted by past experience, personal aesthetic
preferences, the characteristics of the audience, and a good working
knowledge of general perceptual strengths and weaknesses of particular
displays \citep{cleveland:1984,heer:2010}. Perceptual studies are
thinly spread for data visualization, and have, and will probably,
only cover very broad perceptual principles. Faced with design
decisions for a very specific task requires a closer level of
detail. Focus groups \citep{Mazza07} can find small problems with
designs and move us closer to a final handful of possible
designs. Usability studies and case studies
(e.g. \citet{Plaisant:2004}, \citet{Shneiderman:2006}) typically focus
on the use of particular software for solving data exploration tasks.
These approaches lack broad audience validity and
objectiveness. Several papers indicate continuing issues arising with
evaluating information visualizations
\citep{North:2006,Ellis:2006,Viegas:2006,Munzer:2009}.
